\mytitle

### 2023-05-15 chapters/depsynth/synthesis.tex
abstract; more depsynth
Split up big figure

\subsection{The \depsynth Algorithm}

@@

@@

\paragraph{Generating rules from happens-before graphs.}
The \rulesfortest search operates on happens-before graphs,
but its goal is to synthesize dependency rules (\cref{def:dependency-rule}).
The \rulesforgraph procedure (line~\ref{fig:rules:rulesforgraph})
bridges this gap
by taking as input a happens-before graph \gr
and returning a set of dependency rules \ruleset
that are sufficient to enforce the ordering requirements that \gr dictates.
\rulesforgraph uses a simple syntactic approach to generate a rule for each edge in \gr:
if $(w_1, w_2) \in \gr$,
where writes $w_1$ and $w_2$ have labels $l_1 = \langle n_1, t_1 \rangle$ and $l_2 = \langle n_2, t_2 \rangle$, respectively,
then it generates a rule of the form $\deprule{n_2}{n_1}{}$
(reversing the order because $G$ is a happens-before graph
but dependency rules are happens-\emph{after} edges).
To choose an epoch predicate for the generated rule,
we compare the two epochs $t_1$ and $t_2$
and select the predicate that would make the rule match the labels $l_1$ and $l_2$.\tighten

>>>>

\subsection{The \depsynth Algorithm}\label{sec:alg:alg}

@@

\begin{figure}
    \centering
    {\xsmall\input{figs/rulesforgraph.tex}}
    \caption{The procedure for generalizing a happens-before graph \gr into dependency rules
    constructs (at most) one rule for each edge.}
    \label{fig:alg:rulesforgraph}
\end{figure}

@@

\paragraph{Generating rules from happens-before graphs.}
The \rulesfortest search operates on happens-before graphs,
but its goal is to synthesize dependency rules (\cref{def:dependency-rule}).
The \rulesforgraph procedure (\cref{fig:alg:rulesforgraph})
bridges this gap
by taking as input a happens-before graph \gr
and returning a set of dependency rules \ruleset
that are sufficient to enforce the ordering requirements that \gr dictates.
\rulesforgraph uses a simple syntactic approach to generate a rule for each edge in \gr:
if $(w_1, w_2) \in \gr$,
where writes $w_1$ and $w_2$ have labels $l_1 = \langle n_1, t_1 \rangle$ and $l_2 = \langle n_2, t_2 \rangle$, respectively,
then it generates a rule of the form $\deprule{n_2}{n_1}{}$
(reversing the order because $G$ is a happens-before graph
but dependency rules are happens-\emph{after} edges).
To choose an epoch predicate for the generated rule,
we compare the two epochs $t_1$ and $t_2$
and select the predicate that would make the rule match the labels $l_1$ and $l_2$.\tighten
